Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
added figures/CloseDetect.pdf

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges.
A bridge is then picked to aggregate two buildings at time $t$ 
if they become too close.
We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

@@

>>>>

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
These line segments may cross each other or even intersect buildings.
To make the topology simple, 
we only select some of the line segments as bridges.  
We consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are identified as bridges.

At any time $t$, some of the identified bridges are picked to aggregate 
buildings 
which grow to become too close.
The buildings and the bridges already comprise some MSTs.
We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{CloseDetect}
	\caption{bla.}
	\label{fig:CloseDetect}
\end{figure}
